|

### 2021-03-12 documentation/readme.Rmd
Changed paper and userguide names
Update README

PollBasePro is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`.

@@

We also provide `pollbase` and `pollbasepro` as .dta and .sav files for Stata and SPSS users. These files include all necessary value and variable labels and should work seamlessly with both software packages. Click here to download them.

@@

<center><img src="https://raw.githubusercontent.com/jackobailey/econ_half_life/master/documentation/_assets/timeplot_gh.png"></center>

>>>>

PollBasePro is a data package for the `R` programming language. It includes two datasets: `pollbase` and `pollbasepro`. The first provides a long-format and ready-to-analyse version of Mark Pack's dataset of historic British public opinion polls combined with more recent polling data from Wikipedia. The second provides `r format(nrow(pollbasepro), big.mark = ",")` daily estimates of voting intention figures for each of Britain's three largest parties between `r str_remove(format(min(pollbasepro$date), "%d %B %Y"), "^0")` and `r str_remove(format(max(pollbasepro$date), "%d %B %Y"), "^0")`. The user guide and codebook is available [here](https://github.com/jackobailey/PollBasePro/blob/master/download/userguide.pdf) and the accompanying paper is available [here](https://github.com/jackobailey/PollBasePro/blob/master/download/paper.pdf).

@@

We also provide `pollbase` and `pollbasepro` as .dta and .sav files for Stata and SPSS users. These files include all necessary value and variable labels and should work seamlessly with both software packages. [Click here to download them](https://github.com/jackobailey/PollBasePro/tree/master/download).

@@

<center><img src="https://raw.githubusercontent.com/jackobailey/PollBasePro/master/documentation/_assets/timeplot_gh.png"></center>
